
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 12: Predictive Modeling - Part 3"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment12.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Blackboard.

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```


1. Use the `PimaIndiansDiabetes` dataset. Use 15% data for testing. Use cross-validation with of 7 folds to tune random forest `(method='ranger')`.  What are the parameters that produce the greatest accuracy? What is the testing accuracy. 
```{r}
library(mlbench)
library(tidyverse)
library(caret)
library(recipes)
data(PimaIndiansDiabetes)
df <- tibble(PimaIndiansDiabetes)
df = drop_na(df)
df <- df %>% rename(target=diabetes)
df <- df %>% 
  mutate(target = as.factor(target),
         pregnant = as.factor(pregnant),
         pressure = as.factor(pressure),
         triceps = as.factor(triceps),
         age = as.factor(age)
         )
```
```{r}
library(rpart)
set.seed(2020)
splitIndex <- createDataPartition(df$target, p = .85, 
                                  list = FALSE)
df_train <- df[ splitIndex,]
df_test <- df[-splitIndex,]
```
```{r}
tuneGrid = expand.grid(maxdepth = 2:10)
# Tell caret to do Approach 2, i.e. Cross-Validation
trControl = trainControl(method = "cv",
                         number = 7)
# Do Approach 2 
tree_approach2 <- train(target~., data=df_train, 
                                method = "rpart2", 
                                trControl = trControl,
                                tuneGrid = tuneGrid)
getModelInfo('ranger')$ranger$parameters
```



2. Use the `PimaIndiansDiabetes` dataset. Go to https://topepo.github.io/caret/available-models.html and pick a classification model.  Tune the classification model using cross-validation of 7 folds. 
```{r}
tuneGrid = expand.grid(maxdepth = 2:10)
# Tell caret to do Approach 2, i.e. Cross-Validation
trControl = trainControl(method = "cv",
                         number = 7)
# Do Approach 2 
tree_approach2 <- train(target~., data=df_train, 
                                method = "rpart2", 
                                trControl = trControl,
                                tuneGrid = tuneGrid)
getModelInfo('treebag')$treebag$parameters
```


3. (Model Comparison) Use the `PimaIndiansDiabetes` dataset. Pick two models at [this link](https://topepo.github.io/caret/available-models.html) to compare using 7-fold cross validation method. Evaluate the accuracy of the final model on the test data. 


```{r}
tuneGrid = expand.grid(maxdepth = 2:10)
# Tell caret to do Approach 2, i.e. Cross-Validation
trControl = trainControl(method = "cv",
                         number = 7)
# Do Approach 2 
tree_approach2 <- train(target~., data=df_train, 
                                method = "rpart2", 
                                trControl = trControl,
                                tuneGrid = tuneGrid)
getModelInfo('bridge')$bridge$parameters
```


