
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 11: Predictive Modeling - Universal Framework"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment11.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Blackboard.

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```


-------

1. Install the package mlbench and use the follows to import the data

```{r}
library(mlbench)
library(tidyverse)
library(caret)
library(recipes)
data(PimaIndiansDiabetes)
df <- tibble(PimaIndiansDiabetes)
df = drop_na(df)
df <- df %>% rename(target=diabetes)
df <- df %>% 
  mutate(target = as.factor(target),
         pregnant = as.factor(pregnant),
         pressure = as.factor(pressure),
         triceps = as.factor(triceps),
         age = as.factor(age)
         )
```
```{r}
library(rpart)
set.seed(2020)
splitIndex <- createDataPartition(df$target, p = .80, 
                                  list = FALSE)
df_train <- df[ splitIndex,]
df_test <- df[-splitIndex,]
```

Train and Test a decision tree and a random forest with caret. Plot the variable importance of these models. 
```{r}
library(randomForest)
forest_model = randomForest(target ~ ., data=df_train, ntree = 200)
importance(forest_model)
```

2. Train and Test a `glmnet` model. Plot the variable importance of the model. 
```{r}
library(glmnet)
X=cbind(df_train$pregnant,df_train$glucose,df_train$pressure,df_train$triceps,df_train$insulin,df_train$mass,df_train$pedigree,df_train$age)
fit <- glmnet(x=X,y=cbind(df_train$target))
plot(fit)
```

3. Train and test two models that are not `ranger`, `glmnet` or `rpart`  with caret. If possible, plot the variable importance of the model. 

```{r}
forest_model = randomForest(target ~ ., data=df_train, ntree = 200)
plot(forest_model)
```
```{r}
tree_model <- rpart(target ~ ., data = df_train,
                 control = rpart.control(maxdepth = 3))
library(rattle)
fancyRpartPlot(tree_model)
```



